LAGOS lake depth

### 2020-03-26 README.Rmd
use pretty variable names

# see scripts/99_make_taxonomy.R
dt <- read.csv("data/depth_predictors.csv", 
               stringsAsFactors = FALSE) %>% 
  names() %>%  as.data.frame() %>%  setNames("col_name") %>%
  left_join(taxonomy) %>% data.frame() %>%
  dplyr::filter(!is.na(description)) %>%
  setNames(c("column name", "description"))

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# see scripts/99_make_taxonomy.R
dt       <- read.csv("data/00_bathy_depth/00_bathy_depth.csv", 
               stringsAsFactors = FALSE) %>%
  names() %>%  as.data.frame() %>%  setNames("col_name") %>%
  left_join(taxonomy) %>% data.frame() %>%
  dplyr::filter(!is.na(description)) %>%
  setNames(c("column name", "description"))

>>>>

# see scripts/99_make_taxonomy.R
dt <- read.csv("data/depth_predictors.csv", 
               stringsAsFactors = FALSE) %>% 
  names() %>%  as.data.frame() %>%  setNames("col_name") %>%
  left_join(taxonomy) %>% data.frame() %>%
  dplyr::filter(!is.na(description)) %>%
  setNames(c("column name", "description", "variable")) %>%
  select(`column name`, variable, description)

options(knitr.kable.NA = '-')
knitr::kable(dt)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# see scripts/99_make_taxonomy.R
dt       <- read.csv("data/00_bathy_depth/00_bathy_depth.csv", 
               stringsAsFactors = FALSE) %>%
  names() %>%  as.data.frame() %>%  setNames("col_name") %>%
  left_join(taxonomy) %>% data.frame() %>%
  dplyr::filter(!is.na(description)) %>%
  setNames(c("column name", "description", "variable")) %>%
  select(`column name`, variable, description)

@@

### 2020-03-26 figures/02_depth_model.Rmd
use pretty variable names

```{r depth_model_metrics, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.height=2.8, fig.width=4.2}
dt_metrics <- readRDS("../data/01_depth_model/depth_grid_metrics.rds") %>%
  mutate_if(is.numeric, function(x) as.character(round(x, 2))) %>%
  mutate(rsq = as.numeric(rsq)) %>%
  mutate(rsq = case_when(
    as.character(model) == "maxdepth_true_true" ~ NA_real_,
    TRUE ~ rsq)) %>%
  mutate(rmse = case_when(
    as.character(model) == "maxdepth_true_true" ~ "-",
    TRUE ~ rmse)) %>%
  mutate(model = gsub("maxdepth_", "", model)) %>%
  mutate(model = gsub("false", "proxy", model)) %>%
  tidyr::separate(model, c("slope", "distance")) %>%
  dplyr::select(slope, distance, everything(), -.estimator)

@@

```{r 02_depth_model_importance, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.height=3.5, fig.width=8}
dt_fits <- readRDS("../data/01_depth_model/depth_fits.rds")

@@

var_order <- 
  group_by(dt_imp, variable) %>% 
  summarize(max = max(percent_inc_mse)) %>%
  arrange(max) %>%
  pull(variable)
dt_imp$variable <- factor(dt_imp$variable, levels = var_order)

ggplot() + 
  geom_point(data = dt_imp, aes(percent_inc_mse, variable, color = model)) +   
  # geom_hline(linetype = 3, size = 1, colour = "gray", 
  #                yintercept = 1:nlevels(dt$variable)) + 
  theme(text = element_text(family="Times"),
        panel.background = element_blank(), panel.grid = element_blank(),
        panel.border = element_rect(fill = NA), # legend.position = "none", 
        axis.title.x = element_text(family="sans", face = "bold", 
        vjust = -0.5, size = 12), 
        axis.text = element_text(family="sans",size = 11, 
                                 color = "black")) + 
        ylab("") + xlab("Percent Increase in Mean Square Error")
```

>>>>

```{r depth_model_metrics, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.height=2.6, fig.width=4}
dt_metrics <- readRDS("../data/01_depth_model/depth_grid_metrics.rds") %>%
  mutate_if(is.numeric, function(x) as.character(round(x, 2))) %>%
  mutate(rsq = as.numeric(rsq)) %>%
  mutate(rsq = case_when(
    as.character(model) == "maxdepth_true_true" ~ NA_real_,
    TRUE ~ rsq)) %>%
  mutate(rmse = case_when(
    as.character(model) == "maxdepth_true_true" ~ "-",
    TRUE ~ rmse)) %>%
  mutate(model = gsub("maxdepth_", "", model)) %>%
  mutate(model = gsub("false", "proxy", model)) %>%
  tidyr::separate(model, c("slope", "distance")) %>%
  dplyr::select(slope, distance, everything(), -.estimator)

@@

```{r 02_depth_model_importance, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.height=3.2, fig.width=5}
dt_fits      <- readRDS("../data/01_depth_model/depth_fits.rds")
taxonomy_key <- read.csv("../data/taxonomy.csv", stringsAsFactors = FALSE)

@@

var_order <- 
  left_join(dt_imp, taxonomy_key, by = c("variable" = "col_name")) %>%
  group_by(pretty) %>% 
  summarize(max = max(percent_inc_mse)) %>%
  arrange(max) %>%
  pull(pretty)
dt_imp <- left_join(dt_imp, taxonomy_key, by = c("variable" = "col_name")) %>%
  mutate(pretty = factor(pretty, levels = var_order)) %>%
  mutate(variable = pretty) %>%  dplyr::select(-description) %>%
  dplyr::select(-pretty)

ggplot() + 
  geom_point(data = dt_imp, aes(percent_inc_mse, variable, color = model)) +   
  labs(color = "slope-distance\nmeasure") +
  geom_hline(linetype = 3, size = 1, colour = "gray",
                 yintercept = 1:nlevels(dt_imp$variable)) +
  theme(text = element_text(family="Times"),
        panel.background = element_blank(), panel.grid = element_blank(),
        panel.border = element_rect(fill = NA), # legend.position = "none", 
        axis.title.x = element_text(family = "sans", face = "bold", 
        vjust = -0.5, size = 10), 
        axis.text = element_text(family="sans",size = 9, 
                                 color = "black"), 
         legend.key = element_blank()) + 
        ylab("") + xlab("Percent Increase in Mean Square Error")
```

### 2020-03-26 manuscript/figures.Rmd
use pretty variable names

```{r 02_hypso_model_importance, fig.cap = "Recusive Partitioning variable importance.", warning=FALSE, echo = FALSE, eval=FALSE}
knitr::include_graphics("../figures/02_hypso_model_importance-1.pdf")
```

>>>>

```{r 02_hypso_model_importance, fig.cap = "Recusive Partitioning variable importance.", warning=FALSE, echo = FALSE, eval=FALSE, out.extra=''}
knitr::include_graphics("../figures/02_hypso_model_importance-1.pdf")
```

### 2020-03-26 tables/01_predictors.Rmd
use pretty variable names

knitr::kable(dt, digits = 0, format = "markdown") 
```

>>>>

taxonomy_key <- read.csv("../data/taxonomy.csv", stringsAsFactors = FALSE)

dt <- left_join(dt, taxonomy_key, by = c("variable" = "col_name")) %>%
  dplyr::mutate(variable = pretty) %>% select(-pretty, -description)

options(knitr.kable.NA = '-')
knitr::kable(dt, digits = 0, format = "markdown") 
```
